### 2024-08-21 Paper/paper2.tex
Updates from Overleaf

\import{Tables}{MD_noMD_readmort_condition_synth.tex}

@@

While I ultimately employ a synthetic difference-in-differences framework, I also present the coefficient estimates and event study tables under a typical TWFE model specification. That is, there is no weighting of the control group or time periods. Table \ref{tab:forprofit_readmort_fullsample} shows coefficient estimates for the three specifications under Equation \ref{eq:forprofit}. Columns (1)-(3) show coefficient estimates for the weighted average readmission rate outcome, and columns (4)-(6) show coefficient estimates from the weighted average mortality outcome. Generally, these results are qualitatively identical to the synthetic difference-in-difference specification results. There is a statistically significant difference in readmission rate response between for-profits and NFPs with a clinical executive. Specifically, for-profits decrease their readmission rates by .4ppts more than NFPs with a clinical executive. There is no difference (statistically or in magnitude) between readmission rate responses of for-profits compared to all NFPs and NFPs without clincal executives.

Similarly to the synthetic diff-in-diff estimates, there is no statistical difference in mortality between any of the hospital types, but the magnitude difference between for-profits and NFPs with clinical executives is much larger. This oculd be due to the noisiness of mortality as a measure.

\import{Tables}{forprofit_readmort_fullsample.tex}

Further, I present coefficient estimates in Table \ref{tab:MD_noMD_readmort_fullsample} directly comparing NFPs with and without clinical executives for both readmission and mortality rates. Again, these results are very similar to the main results of the paper, with only slightly larger magnitudes. NFPs without a clinical executive respond to the pay-for-performance incentives by decreasing readmission and mortality rates more aggressively than NFPs with clinical executives.

\import{Tables}{MD_noMD_readmort_fullsample.tex}

Finally, I present these results in typical event study form in Figure \ref{fig:es_plot}, which show no evidence of significant pre-trends driving the findings.

\begin{figure}[ht!]
     \caption{TWFE Event Study Results}
     \centering
          \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{}
         \includegraphics[width=\textwidth]{Objects/read_forprofit_es_graph.pdf}
         \label{fig:es_plota}
     \end{subfigure}%
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{}
         \includegraphics[width=\textwidth]{Objects/read_MD_es_graph.pdf}
         \label{fig:es_plotb}
     \end{subfigure}%
     \vspace{5mm}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{}
         \includegraphics[width=\textwidth]{Objects/mort_forprofit_es_graph.pdf}
         \label{fig:es_plotc}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.45\textwidth}
         \centering
         \caption{}
         \includegraphics[width=\textwidth]{Objects/mort_MD_es_graph.pdf}
         \label{fig:es_plotd}
     \end{subfigure}
        \label{fig:es_plot}
    \end{figure}

>>>>

\import{Tables}{condition_synthdid_table.tex}

@@

\subsubsection{Effect of Clinically Trained Executives on Response to Financial Incentive on Quality}

\import{Tables}{main_twfe_match_tab.tex}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=.99\linewidth]{Objects/main_twfe_match_eventstudy.pdf}
    \caption{Effect of Clinical Executives; Event Study Results}
    \label{fig:main_twfe_match_es}
\end{figure}

### 2024-08-21 Tables/condition_synthdid_table.tex
Updates from Overleaf

\caption{\label{tab:results_by_condition}Effect of Clinically Trained Executive on Condition-Specific Readmission and Mortality Rates}
\centering
\begin{tabular}[t]{lccclcc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Readmission Rates} & \multicolumn{3}{c}{Mortality Rates} \\
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{AMI} & \multicolumn{1}{c}{HF} & \multicolumn{1}{c}{Pneum.} & \multicolumn{1}{c}{AMI} & \multicolumn{1}{c}{HF} & \multicolumn{1}{c}{Pneum.} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6} \cmidrule(l{3pt}r{3pt}){7-7}
 & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
Ever Clinical Exec x Post Program & 0.25 & 0.14 & 0.46$^{**}$ & -0.13 & 0.03 & 0.3\\
 & (0.18) & (0.18) & (0.14) & (0.19) & (0.13) & (0.19)\\
 &  &  &  &  &  & \\
Hospital FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
Year FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\addlinespace
Observations & 1,135 & 1,640 & 1,635 & 1,300 & 1,640 & 1,635\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:results_by_condition}Effect of Clinically Trained Executive on Condition-Specific Readmission and Mortality Rates}
\centering
\begin{tabular}[t]{lcccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Readmission Rates} & \multicolumn{3}{c}{Mortality Rates} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7}
\addlinespace[0.3em]
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{AMI} & \multicolumn{1}{c}{HF} & \multicolumn{1}{c}{Pneum.} & \multicolumn{1}{c}{AMI} & \multicolumn{1}{c}{HF} & \multicolumn{1}{c}{Pneum.} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5} \cmidrule(l{3pt}r{3pt}){6-6} \cmidrule(l{3pt}r{3pt}){7-7}
 & (1) & (2) & (3) & (4) & (5) & (6)\\
\midrule
Always Clinical Exec x Post Program & 0.25 & 0.14 & 0.46$^{**}$ & -0.13 & 0.03 & 0.3\\
 & (0.18) & (0.18) & (0.14) & (0.19) & (0.13) & (0.19)\\
 &  &  &  &  &  & \\
Hospital FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
Year FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\addlinespace
Observations & 1,135 & 1,640 & 1,635 & 1,300 & 1,640 & 1,635\\
\bottomrule
\multicolumn{7}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{7}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

### 2024-08-21 Tables/main_twfe_match_tab.tex
Updates from Overleaf

\caption{\label{tab:main_twfe_match}Effect of Clinically Trained Executive, TWFE and Matched Sample}
\centering
\begin{tabular}[t]{lcccl}
\toprule
\multicolumn{1}{c}{\underline{ }} & \multicolumn{2}{c}{\underline{TWFE}} & \multicolumn{2}{c}{\underline{Matched Sample}} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{Read} & \multicolumn{1}{c}{Mort} & \multicolumn{1}{c}{Read} & \multicolumn{1}{c}{Mort} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5}
 & (1) & (2) & (3) & (4)\\
\midrule
Ever Clinical Exec x Post Program & 0.42$^{**}$ & 0.11 & 0.65$^{*}$ & 0.03\\
 & (0.15) & (0.15) & (0.3) & (0.4)\\
 &  &  &  & \\
Hospital FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
Year FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\addlinespace
Observations & 2,387 & 2,381 & 1,025 & 1,023\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{5}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:main_twfe_match}Effect of Clinically Trained Executive; TWFE and Matched Sample}
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{\underline{ }} & \multicolumn{2}{c}{TWFE} & \multicolumn{2}{c}{Matched Sample} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
\addlinespace[0.3em]
\multicolumn{1}{c}{ } & \multicolumn{1}{c}{Readmission} & \multicolumn{1}{c}{Mortality} & \multicolumn{1}{c}{Readmission} & \multicolumn{1}{c}{Mortality} \\
\cmidrule(l{3pt}r{3pt}){2-2} \cmidrule(l{3pt}r{3pt}){3-3} \cmidrule(l{3pt}r{3pt}){4-4} \cmidrule(l{3pt}r{3pt}){5-5}
 & (1) & (2) & (3) & (4)\\
\midrule
Always Clinical Exec x Post Program & 0.42$^{**}$ & 0.11 & 0.65$^{*}$ & 0.03\\
 & (0.15) & (0.15) & (0.3) & (0.4)\\
 &  &  &  & \\
Hospital FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
Year FE & $\checkmark$ & $\checkmark$ & $\checkmark$ & $\checkmark$\\
\addlinespace
Observations & 2,387 & 2,381 & 1,025 & 1,023\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{5}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}
